%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  File name: outlook.tex
%  Version: 18.08.2019 (hve)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\addcontentsline{toc}{chapter}{Outlook}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Outlook}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Our discussion on the foundations of statistical methods of data
analysis and their application to specific quantitative problems
ends here. We have focused on the description of uni- and bivariate
data sets and making inferences from corresponding random samples
within the frequentist approach to Probability Theory. At this
stage, the attentive reader should feel well-equipped for
confronting problems concerning more complex, multivariate data
sets, and adequate methods for tackling them by statistical means.
Many modules at the Master degree level review a broad spectrum of
advanced topics such as multiple linear regression, generalised
linear models, principal component analysis, or cluster analysis,
which in turn relate to computational techniques presently employed
in the context of machine learning. The ambitious reader might even
think of getting involved with proper research and work towards a
Ph.D.~degree in an empirical scientific discipline. To gain
additional data analytical flexibility, and to increase chances on
obtaining transparent and satisfactory research results, it is
strongly recommended to consult the conceptually compelling
inductive Bayes--Laplace approach to statistical inference. In
order to leave behind the methodological shortcomings uncovered by
the recent replication crisis (cf., e.g., Refs.~\ct{eco2013},
\ct{nuz2014}, or \ct{vas2017}), strict adherence to accepted
scientific standards cannot be compromised with.\footnote{With
regard to the replication crisis, the interested reader might be
aware of the international initiative known as the Open Science
Framework. URL (cited on August 17, 2019):
\href{https://osf.io}{https://osf.io}.}

\medskip
\noindent
Beyond activities within the scientific community, the dedicated
reader may feel encouraged to use her/his solid topical
qualification in statistical methods of data analysis for careers
in either field of higher education, public health, renewable
energy supply chains, evaluation of climate change adaptation,
development of plans for sustainable production in agriculture and
global economy, civil service, business management, marketing,
logistics, or the financial services, amongst a multitude of other
inspirational possibilities.

\medskip
\noindent
Not every single matter of human life is amenable to
quantification, or, acknowledging an individual freedom of making
choices, needs to be quantified in the first place. Blind faith in
the powers of quantitative methods is certainly misplaced. Thorough reflection and introspection on the options available for action
and their implied consequences, together with a critical evaluation
of relevant tangible facts, might suggest a viable alternative
approach to a given research or practical problem. Generally, there
is a potential for looking behind curtains, shifting horizons,
or anticipating prospects and opportunities. Finally, more often
than not, there exists a dimension of non-knowledge on the part of
the individual investigator that needs to be taken into account as
an integral part of the boundary conditions of the overall problem
in question.  The adventurous mind will always excel in view of the
intricate challenge of making inferences on the basis of incomplete 
information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%